Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-08-16 manuscript/supplemental_material.Rnw
increase headheight
switch to plot ancestral state trees

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,style=nature,citestyle=numeric-comp,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=blue,citecolor=blue]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\usepackage{cleveref}
\usepackage{xspace}
\newenvironment{narrow}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{#1}%
      \setlength{\rightmargin}{#2}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{\parindent}%
      \setlength{\parsep}{\parskip}}%
  \item[]}{\end{list}}
\def\newblock{\hskip}
\newenvironment{paperquote}{%
  \begin{quote}%
     \it
  }%
  {\end{quote}}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
\newenvironment{enumerate*}%
  {\begin{enumerate}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{enumerate}}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
\oddsidemargin 0.0in 
\textwidth 6.5in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}

@@

<<source.to.latex,echo=FALSE,message=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R")))>>=
for (a in paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R"))) {
    source(a)
}
@

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CRH" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 min.fpkm=1,
                 axis.text.size=5,
                 axis.text.angle=0,
                 fontsize=6.5
                 )
@ 
\caption{\genetreeexplanation{\textit{CRH}}}
\label{fig:crh_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="ADAM12" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,
                 gene.tree.expression,
                 subtree=c("ENSMODG00000010538","ENSSSCG00000010746"),
                 min.fpkm=0.1,
                 axis.text.size=4,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation{\textit{ADAM12}}}
\label{fig:adam12_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="KISS1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 min.fpkm=0.1,
                 axis.text.size=5,
                 axis.text.angle=0,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation[0.1]{\textit{KISS1}}}
\label{fig:kiss1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PAPPA" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSSSCG00000005498","ENSG00000182752"),
                 min.fpkm=0.1,
                 axis.text.size=5,
                 axis.text.angle=0,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation[0.1]{\textit{PAPPA}}}
\label{fig:pappa_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="TGFB1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 subtree=c("ENSMODG00000008630","ENSSSCG00000026296"),
                 gene.tree.table,gene.tree.expression,
                 min.fpkm=1,
                 axis.text.size=3.5,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation{\textit{TGFB1}}}
\label{fig:tgfb1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="GPC3" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,
                 subtree=c("ENSCAFG00000018864","ENSLAFG00000025706"),
                 gene.tree.expression,
                 min.fpkm=1,
                 axis.text.size=3.5,
                 fontsize=6
                 )
@ 
\caption{\genetreeexplanation{\textit{GPC3}}}
\label{fig:gpc3_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="FSTL1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,
                 gene.tree.expression,
                 min.fpkm=1,
                 axis.text.size=3.5,
                 fontsize=5
                 )
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTL1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="SERPINE2" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,
                 gene.tree.expression,
                 min.fpkm=1,
                 axis.text.size=3.5,
                 fontsize=3)
@ 
\caption{\genetreeexplanation{\textit{SERPINE2}}}
\label{fig:serpine_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_id=="ENSCAFG00000010638" & species=="canis familiaris",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=5)
@ 
\caption{\genetreeexplanation{\textit{SSLP1}}}
\label{fig:sslp1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CYP19A1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=4.5)
@ 
\caption{\genetreeexplanation{estrogen synthesis genes}}
\label{fig:estrogen_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="HSD3B1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSMODG00000005385","ENSLAFG00000027896"),
                 axis.text.size=3.5,
                 fontsize=4.5
                 )
@ 
\caption{\genetreeexplanation{progesterone synthesis genes}}
\label{fig:progesterone_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="CSH1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=4)
@ 
\caption{\genetreeexplanation{chorionic somatomammotropin}}
\label{fig:csh1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PRL" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=3.5)
@ 
\caption{\genetreeexplanation{prolactin}}
\label{fig:prolactin_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="RLN2" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=3.5)
@ 
\caption{\genetreeexplanation{\textit{RLN2}}}
\label{fig:rln2_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree["ENSDNOG00000033320",tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSDNOG00000033320","ENSMODG00000017988"),
                 axis.text.size=3.5,
                 fontsize=4)
@ 
\caption{\genetreeexplanation{\cow \textit{OVOS2}}}
\label{fig:ovos2_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PRLR" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSG00000113494","ENSMODG00000020376"),
                 axis.text.size=3.5,
                 fontsize=4)
@ 
\caption{\genetreeexplanation{prolactin receptor, \textit{PRLR}}}
\label{fig:prolactin_receptor_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="HOXA11" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSBTAG00000014738","ENSECAG00000013229"),
                 axis.text.size=3.5,
                 fontsize=4
                 )
@ 
\caption{\genetreeexplanation{\textit{HOXA11}}}
\label{fig:hoxa11_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="HBE1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,
                 subtree=c("ENSBTAG00000037815",
                           "ENSMUSG00000078621"),
                 axis.text.size=3.5,
                 fontsize=4)
@ 
\caption{\genetreeexplanation{\textit{HBE1}}}
\label{fig:hbe1_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="NPPB" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=6
                 )
@ 
\caption{\genetreeexplanation{\textit{NPPB}}}
\label{fig:nppb_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="NPPC" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=3
                 )
@ 
\caption{\genetreeexplanation{\textit{NPPC}}}
\label{fig:nppc_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="LGALS1" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=3.5
                 )
@ 
\caption{\genetreeexplanation{\textit{LGALS1} and \textit{LGALS2}}}
\label{fig:galectins_evolution_tree}
\end{figure}

@@

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="LGALS13" & species=="homo sapiens",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),gene.tree.table,gene.tree.expression,
                 axis.text.size=3.5,
                 fontsize=4.5
                 )
@ 
\caption{\genetreeexplanation{\textit{LGALS13}}}
\label{fig:galectins_lgals13_evolution_tree}
\end{figure}

>>>>

\documentclass[english,12pt]{article}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=15pt]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage[backend=biber,natbib=true,hyperref=true,style=nature,citestyle=numeric-comp,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=blue,citecolor=blue]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads,nofighead,notabhead]{endfloat}
% \AtBeginFigures{\section*{Figure Legends}\renewcommand{\efloatseparator}{\hbox{}}}
% \AtBeginTables{\section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\usepackage[x11names,svgnames]{xcolor}
\usepackage{texshade}
\usepackage{tikz}
\usepackage{nameref}
\usepackage{zref-xr,zref-user}
\usepackage{cleveref}
\usepackage{xspace}
\newenvironment{narrow}[2]{%
  \begin{list}{}{%
      \setlength{\topsep}{0pt}%
      \setlength{\leftmargin}{#1}%
      \setlength{\rightmargin}{#2}%
      \setlength{\listparindent}{\parindent}%
      \setlength{\itemindent}{\parindent}%
      \setlength{\parsep}{\parskip}}%
  \item[]}{\end{list}}
\def\newblock{\hskip}
\newenvironment{paperquote}{%
  \begin{quote}%
     \it
  }%
  {\end{quote}}
\renewcommand{\textfraction}{0.15}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
\newenvironment{enumerate*}%
  {\begin{enumerate}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{enumerate}}
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}
\oddsidemargin 0.0in 
\textwidth 6.5in
\raggedbottom
\clubpenalty = 10000
\widowpenalty = 10000
% make the afill smaller
\renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
\pagestyle{fancy}

@@

<<source.to.latex,echo=FALSE,message=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R","plot_ancestral_state_tree.R")))>>=
for (a in paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R",
                                       "utility_functions.R",
                                       "plot_ancestral_state_tree.R"))) {
    source(a)
}
@

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CRH" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.37))
@ 
\caption{\genetreeexplanation{\textit{CRH}}}
\label{fig:crh_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="ADAM12" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c("ENSMODG00000010538","ENSSSCG00000010746"),
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.25))
@ 
\caption{\genetreeexplanation{\textit{ADAM12}}}
\label{fig:adam12_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="KISS1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.7))
@ 
\caption{\genetreeexplanation[0.1]{\textit{KISS1}}}
\label{fig:kiss1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PAPPA"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSSSCG00000005498","ENSG00000182752"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.15))
@ 
\caption{\genetreeexplanation[0.1]{\textit{PAPPA}}}
\label{fig:pappa_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="TGFB1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSMODG00000008630","ENSSSCG00000026296"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.3))
@ 
\caption{\genetreeexplanation{\textit{TGFB1}}}
\label{fig:tgfb1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="GPC3"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSCAFG00000018864","ENSLAFG00000025706"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.13))
@ 
\caption{\genetreeexplanation{\textit{GPC3}}}
\label{fig:gpc3_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="FSTL1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=5,color="black",fontface="italic")+xlim(0,3))
@ 
\caption{\genetreeexplanation{follistatin-like 1 \textit{FSTL1}}}
\label{fig:fstl1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="SERPINE2"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000008717",
                                          "ENSMODG00000004913"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=4,color="black",fontface="italic")+xlim(0,0.8))
@ 
\caption{\genetreeexplanation{\textit{SERPINE2}}}
\label{fig:serpine_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_id=="ENSCAFG00000010638" &
                                                    species=="canis familiaris"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1.2))
@ 
\caption{\genetreeexplanation{\textit{SSLP1}}}
\label{fig:sslp1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CYP19A1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.37))
@ 
\caption{\genetreeexplanation{estrogen synthesis genes}}
\label{fig:estrogen_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HSD3B1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSMODG00000005385","ENSLAFG00000027896"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.6))
@ 
\caption{\genetreeexplanation{progesterone synthesis genes}}
\label{fig:progesterone_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CSH1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.9))
@ 
\caption{\genetreeexplanation{chorionic somatomammotropin}}
\label{fig:csh1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PRL"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=3,color="black",fontface="italic")+xlim(0,1))
@ 
\caption{\genetreeexplanation{prolactin}}
\label{fig:prolactin_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="RLN2"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.8))
@ 
\caption{\genetreeexplanation{\textit{RLN2}}}
\label{fig:rln2_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_id=="ENSDNOG00000033320"),
                                subtree=c("ENSDNOG00000033320","ENSMODG00000017988"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=5,color="black",fontface="italic")+xlim(0,1.3))
@ 
\caption{\genetreeexplanation{\cow \textit{OVOS2}}}
\label{fig:ovos2_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PRLR"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSG00000113494","ENSMODG00000020376"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.3))
@ 
\caption{\genetreeexplanation{prolactin receptor, \textit{PRLR}}}
\label{fig:prolactin_receptor_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HOXA11"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000014738","ENSECAG00000013229"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.4))
@ 
\caption{\genetreeexplanation{\textit{HOXA11}}}
\label{fig:hoxa11_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="HBE1"
                                                    & species=="homo sapiens"),
                                subtree=c("ENSBTAG00000037815",
                                          "ENSMUSG00000078621"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=4,color="black",fontface="italic")+xlim(0,0.6))
@ 
\caption{\genetreeexplanation{\textit{HBE1}}}
\label{fig:hbe1_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="NPPB"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.4))
@ 
\caption{\genetreeexplanation{\textit{NPPB}}}
\label{fig:nppb_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="NPPC"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,0.32))
@ 
\caption{\genetreeexplanation{\textit{NPPC}}}
\label{fig:nppc_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="LGALS1"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1))
@ 
\caption{\genetreeexplanation{\textit{LGALS1} and \textit{LGALS2}}}
\label{fig:galectins_evolution_tree}
\end{figure}

@@

print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="LGALS13"
                                                    & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                trees=trees
                                )+
      geom_tiplab(size=6,color="black",fontface="italic")+xlim(0,1.5))
@ 
\caption{\genetreeexplanation{\textit{LGALS13}}}
\label{fig:galectins_lgals13_evolution_tree}
\end{figure}
